Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam

### 2022-03-25 analysis/paper/paper.Rmd
New updates and sources for environmental context

While early hominins reached Mainland Southeast Asia as early as 800 ka ago (Forestier et al., 2022), the

Mainland Southeast Asia 
-Further context from (McAdams et al, 2020)

@@

@@

>>>>

While early hominins reached Mainland Southeast Asia as early as 800 ka ago (Forestier et al., 2022), the oldest skeletal remains of anatomically modern humans date to roughly 50-70 ka ago (Demeter et al., 2017; Shackelford et al., 2018).

Mainland Southeast Asia 
-Further context from (McAdams et al., 2020)

@@

Demeter, F., Shackelford, L., Westaway, K., Barnes, L., Duringer, P., Ponche, J.-L., Dumoncel, J., Sénégas, F., Sayavongkhamdy, T., Zhao, J.-X., Sichanthongtip, P., Patole-Edoumba, E., Dunn, T., Zachwieja, A., Coppens, Y., Willerslev, E., & Bacon, A.-M. (2017). Early Modern Humans from Tam Pà Ling, Laos: Fossil Review and Perspectives. Current Anthropology, 58(S17), S527–S538. https://doi.org/10.1086/694192

@@

Shackelford, L., Demeter, F., Westaway, K., Duringer, P., Ponche, J.-L., Sayavongkhamdy, T., Zhao, J.-X., Barnes, L., Boyon, M., Sichanthongtip, P., Sénégas, F., Patole-Edoumba, E., Coppens, Y., Dumoncel, J., & Bacon, A.-M. (2018). Additional evidence for early modern human morphological diversity in Southeast Asia at Tam Pa Ling, Laos. Quaternary International, 466, 93–106. https://doi.org/10.1016/j.quaint.2016.12.002
